Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-01-12 tex/sections/blocks.tex
Fix readability issues of Subsection "Consensus"
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

For validating the previous block, instead of directly validating the contents of the block, a validator only
verifies the block certificates. Each block of the Argennon blockchain has two certificates: the certificate of
validators, $v \mhyphen cert$, and the certificate of the delegates, $d \mhyphen cert$. Verifying $d \mhyphen
cert_{h-1}$ is straightforward but verifying $v \mhyphen cert_{h-1}$ is more challenging. $v \mhyphen cert_{h-1}$ is an
aggregate signature and validating it requires accessing the AscEE heap state at block $h-1-m$, where $m$ is the
total number of validator assemblies, to obtain public keys and stake values. Again, in addition to direct
verification, a validator can use computational integrity proofs, received from the Argennon cloud, to perform
cheaper verification of this certificate.

The block at height $h$ includes a certificate of validators for block $h-k$ which is used to record the participation
of validators and facilitate reward calculation. This certificate needs to be validated based on stake and public key
database at block $h-k-m$, and can be cheaply done by using computational proofs, obtained from the Argennon cloud.
Here $k$ is the maximum allowed length of the unvalidated part of the Argennon blockchain. (See
Section~\ref{subsec:validators-committee})

This type of block validation only validates the transition from block $h-1$ to block $h$, and the block is valid
only if its previous block is valid. We
call this type of block validation \emph{conditional block validation}, since the validity of the current block is
conditioned on the validity of the previous block.

@@

In summary, a validator validates a block by verifying three computational integrity proofs: $\pi_{\tau}$ which proves
the transition is correct, $\pi_{h-1}$ which proves the previous block has a correct certificate of validators and
$\pi_{h-k}$ which proves the validity of the included certificate of validators of block $h-k$. It should be noted that
these proofs are not part of the block contents and therefore the exact argument system used for generating them is
not specified by the Argennon protocol.

>>>>

For validating the previous block, instead of directly validating the contents of the block, a validator only
verifies the block certificates. Each block of the Argennon blockchain has two certificates: the certificate of
validators, $v \mhyphen cert$, and the certificate of delegates, $d \mhyphen cert$. Verifying $d \mhyphen
cert_{h-1}$ is straightforward but verifying $v \mhyphen cert_{h-1}$ is more challenging. $v \mhyphen cert_{h-1}$ is an
aggregate signature and validating it requires accessing the AscEE heap state at block~$h-1-m$, where $m$ is the
total number of validator assemblies, to obtain public keys and stake values. Again, in addition to direct
verification, a validator can use computational integrity proofs, received from the Argennon cloud, to perform
cheaper verification of this certificate.

The block at height~$h$ includes a certificate of validators for block~$h-k$ which is used to record the participation
of validators and facilitate reward calculation. This certificate needs to be validated based on stake and public key
database at block~$h-k-m$, and can be cheaply done by using computational proofs, obtained from the Argennon cloud.
Here $k$ is the maximum allowed length of the unvalidated part of the Argennon blockchain. (See
Section~\ref{subsec:validators-committee})

This type of block validation only validates the transition from block~$h-1$ to block~$h$, and the block is valid
only if its previous block is valid. We
call this type of block validation \emph{conditional block validation}, since the validity of the current block is
conditioned on the validity of the previous block.

@@

In summary, a validator validates a block by verifying three computational integrity proofs: $\pi_{\tau}$ which proves
the transition is correct, $\pi_{h-1}$ which proves the previous block has a correct certificate of validators and
$\pi_{h-k}$ which proves the validity of the included certificate of validators of block~$h-k$. It should be noted that
these proofs are not part of the block contents and therefore the exact argument system used for generating them is
not specified by the Argennon protocol.

### 2023-01-12 tex/sections/consensus.tex
Fix readability issues of Subsection "Consensus"
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the assembly of validators. A block is considered final after its \textbf{next} block receives \textbf{both} of
its certificates. In Argennon as long as more than half of the total stake of validators is controlled by honest users,
the probability of discarding a final block is near zero even if all the delegates are malicious.

In addition to primary committees, Argennon has several community driven committees. Certificates of these
committees are not required for block finality, but they could be used by members of validator assemblies to better
decide about the validity of a block.

@@

The committee of delegates is a small committee of trusted delegates, elected by Argennon users through the
Argennon Decentralized Autonomous Governance system (ADAGs\footnote{pronounced \textipa{/eI-dagz/}.}).
At the start of the Argennon main-net, this committee will be elected for one-year terms and will have five members.
Later, this could be changed by the ADAGs in a procedure described in Section~\ref{sec:adags}.

@@

Besides the main committee, a reserve committee of delegates consisting of three members is elected by users
either through the ADAGs or by \emph{emergency agreement} during the recovery protocol. In case the main committee
fails to generate new blocks or behaves maliciously, the task of
block generation will be assigned to the reserve committee until the main committee comes back online or a new
committee is elected through the ADAGs.

@@

The committee of delegates may use any type of agreement protocol to reach consensus on the
next block. Usually the delegates are large organizations, and they can communicate with each
other efficiently using their reliable networking infrastructure. This mostly eliminates the complications of their
consensus protocol and any protocol could have a good performance in practice. Usually a very simple and fast protocol
can do the job: one of the members is randomly chosen as the proposer, and other members vote ``yes'' or ``no'' on the
proposed block. For better performance, the delegates should run their agreement protocol for reaching consensus about
small batches of transactions in their mem-pools, instead of the whole next block.

If one of the delegates loses its network connectivity, no new blocks can be generated. For this reason,
the delegates should invest on different types of communication infrastructure, to make sure they will never lose
connectivity to each other and to the Argennon network.

@@

The Argennon protocol calculates a stake value for every account, which is an estimate of a user's stake in the
system, and is measured in ARGs. Any account whose stake value is higher than
\texttt{minValidatorStake} threshold is considered a \emph{validator}.
The \texttt{minValidatorStake}
threshold is determined by the ADAGs, but it can never be higher than $1000$ ARGs.

@@

Every validator has a status which can be either \texttt{online} or \texttt{offline}.
This status is stored in the ARG smart contract and is part of the staking database. A validator can change
his status to \texttt{offline} through an external request (transaction) to the ARG application. In this request he
exactly specifies for how long he wants to be offline and after this period his status will be automatically considered
\texttt{online} again. When a validator sets his status to \texttt{offline} for some period of time, he
will receive a small portion of the maximum possible reward that a validator can receive in that period of time by
actively participating in the consensus protocol. This ensures that a validator has an incentive for changing his
status to offline rather than simply becoming inactive.

@@

There is no transaction type for changing the status of a validator to \texttt{online}. A malicious delegates committee
would be able to censor this type of transactions and prevent honest validators from coming back online. For this reason
the status of a validator is considered online automatically when the specified period of time for being offline ends.

@@

The merging will continue recursively until the online stake of all remaining assemblies is higher than
\texttt{minOnlineStake} fraction.
If eventually all assemblies get merged together and only one assembly remains, the condition
for validity of block certificates changes: A certificate of validators will be considered valid if the sum of stakes
of the certificate signers is higher than $2/3$ of the total stake of validators and \texttt{online/offline}
status of validators becomes ineffective.

@@

Consequently, in Argennon the block validation by assemblies is performed in parallel, and validators
do not wait for seeing the validators certificate of the previous block to start block validation. On the
other hand, the block certificates are published and broadcast sequentially. A validator does not publish his
signature, if the certificate of the previous block validator assembly has not been published yet. This ensures that
an invalid fork made by malicious delegates will not receive any certificates from any validator assemblies.

@@

We analyze the minimum amount of stake that is required for conducting different types of attacks against the Argennon
blockchain. In these attack scenarios, we assume that a single validator assembly is corrupted, all the delegates
are malicious and the adversary is able to fully control message transmission and partition the network arbitrarily.

We denote the total stake of the corrupted validator assembly with $s$ and the total stake of malicious users of the
assembly with $m$. We use $d$ to denote the stake of users of the assembly who have \texttt{offline} status and $h$
to denote the stake of users of the assembly who have \texttt{online} status and do not participate in the
protocol.\footnote{$d$ stands for \emph{deactivated} and $h$ stands for \emph{hidden}.} We assume
that a certificate is accepted if it is signed by more than $r$ fraction of the total online stake of the assembly.
We obtain the minimum required malicious stake for three types of attacks:
\begin{itemize}
    \item Confirming an invalid block:
    \[ m > r(s-d) \]
    \item Forking the blockchain by double voting and network partitioning:
    \[m > (2r-1)(s-d)+h \]
    \item Halting the blockchain by refusing to vote:
    \[m > (1-r)(s-d)-h \]
\end{itemize}

In Argennon we have $r=\frac{3}{4}$ and $d < \frac{1}{3}s$.
Consequently, in Argennon to confirm an invalid block, the adversary needs at least $\frac{1}{2}$ of the total stake
of an assembly. For forking the blockchain, interestingly $m$ is
minimized when $h=0$, and $\frac{1}{3}s$ is the minimum required stake. For halting the blockchain,
an adversary requires a stake higher than $\frac{1}{6}s-h$.

@@

To compare the minimum stake required for halting the blockchain in two protocols, we can solve the following
inequality:
\[
    \frac{1}{4}(s-d)-h > \frac{1}{3}s-(d+h)\ \cdot
\]
We observe that as long as $d>\frac{1}{9}s$, the minimum required stake for halting the blockchain is higher in the
Argennon protocol and the value of $h$ does not matter.

>>>>

Every block of the Argennon blockchain needs a certificate from both the committee of delegates and
the assembly of validators. A block is considered final after its \textbf{next} block receives \textbf{both} of
its certificates. In Argennon as long as more than $2/3$ of the total stake of validators is controlled by honest users,
the probability of discarding a final block is zero even if all the delegates are malicious.

In addition to primary committees, Argennon could have several community driven committees. Certificates of these
committees are not required for block finality, but they could be used by members of validator assemblies to better
decide about the validity of a block.

@@

The committee of delegates is a small committee of trusted delegates, elected by Argennon users through the
Argennon Decentralized Autonomous Governance system (ADAGs\footnote{pronounced \textipa{/eI-dagz/}.}).
At the start of the Argennon main-net, this committee will be elected for one-year terms and will have five members.
Later, this can be changed by the ADAGs in a procedure described in Section~\ref{sec:adags}.

@@

Besides the main committee, a reserve committee of delegates consisting of three members is elected by validators
either through the ADAGs or by the \emph{emergency agreement} during the recovery protocol. In case the main committee
fails to generate new blocks or behaves maliciously, the task of
block generation will be assigned to the reserve committee until the main committee comes back online or a new
committee is elected through the ADAGs.

@@

The committee of delegates may use any type of agreement protocol to reach consensus on the
next block. Usually the delegates are large organizations, and they can communicate with each
other efficiently using their reliable networking infrastructure. This mostly eliminates the complications of their
consensus protocol and any protocol could have a good performance in practice. Usually a very simple and fast protocol
can do the job: one of the members is randomly chosen as the proposer, and other members vote ``yes'' or ``no'' on the
proposed block. For better performance, the delegates should run their agreement protocol for reaching consensus about
small batches of transactions in their mem-pools, instead of the whole block.

If one of the delegates loses its network connectivity, no new blocks can be generated until the reserve committee
gets activated. For this reason, the delegates should invest on different types of communication infrastructure, to
make sure they will never lose connectivity to each other and to the Argennon network.

@@

The Argennon protocol calculates a stake value for every account, which is an estimate of a user's stake in the
system, and is measured in ARGs. Any account whose stake value is higher than
\texttt{minValidatorStake} threshold is considered a \emph{validator}.
The \texttt{minValidatorStake}
threshold is determined by the ADAGs, but it can never be higher than $1000$ ARG\@.

@@

Every validator has a status which can be either \texttt{online} or \texttt{offline}.
This status is stored in the ARG application and is part of the staking database. A validator can change
his status to \texttt{offline} through an external request (transaction) to the ARG application. In this request he
exactly specifies for how long he wants to be offline and after this period his status will be automatically considered
\texttt{online} again. When a validator sets his status to \texttt{offline} for some period of time, he
will receive a small portion of the maximum possible reward that a validator can receive in that period of time by
actively participating in the consensus protocol. This ensures that a validator has an incentive for changing his
status to offline rather than simply becoming inactive.

@@

There is no transaction type for changing the status of a validator to \texttt{online}. A malicious committee
of delegates would be able to censor this type of transactions and prevent honest validators from coming back online.
For this reason the status of a validator is considered online automatically when the specified period of time for
being offline ends.

@@

The merging will continue recursively until the online stake of all remaining assemblies is higher than
\texttt{minOnlineStake} fraction.
If eventually all assemblies get merged together and only one assembly remains, the condition
for validity of block certificates changes: A certificate of validators will be considered valid if the sum of stakes
of the certificate signers is higher than $2/3$ of the total stake of validators and \texttt{online/offline}
status of validators becomes ineffective. This prevents the system from going into temporary deadlocks and the
community will always be able to preserve the liveliness without waiting for the expiration of offline status of
some accounts.

@@

Consequently, in Argennon the block validation by assemblies is performed in parallel, and validators
do not wait for seeing the validators certificate of the previous block to start block validation. On the
other hand, the block certificates are published and broadcast sequentially. A validator does not publish his vote,
if the certificate of the validator assembly of the previous block has not been published yet. This ensures
that an invalid fork made by malicious delegates can not receive any valid certificates from any validator assemblies.

@@

We analyze the minimum amount of stake that is required for conducting different types of attacks against the Argennon
blockchain. In these attack scenarios, we assume that a single validator assembly is corrupted, all the delegates
are malicious and the adversary is able to fully control message transmission between nodes and partition the network
arbitrarily.

We denote the total stake of the corrupted validator assembly with $s$ and the total stake of malicious users of the
assembly with $m$. We use $d$ to denote the stake of users of the assembly who have \texttt{offline} status and $h$
to denote the stake of users of the assembly who have \texttt{online} status and do not participate in the
protocol.\footnote{$d$ stands for \emph{deactivated} and $h$ stands for \emph{hidden}.} We assume
that a certificate is accepted if it is signed by more than $r$ fraction of the total online stake of the assembly.
We obtain the minimum required malicious stake for three types of attacks:
\begin{itemize}
    \item Certifying an invalid block:
    \[ m > r(s-d) \]
    \item Forking the blockchain by double voting and network partitioning:
    \[m > (2r-1)(s-d)+h \]
    \item Halting the blockchain by refusing to vote:
    \[m > (1-r)(s-d)-h \]
\end{itemize}

In Argennon we have $r=\frac{3}{4}$ and $d < \frac{1}{3}s$.
Consequently, in Argennon to confirm an invalid block, the adversary needs at least $\frac{1}{2}$ of the total stake
of an assembly. For forking the blockchain, interestingly $m$ is
minimized when $h=0$, thus the minimum required stake is $\frac{1}{3}s$. For halting the blockchain,
an adversary requires a stake higher than $\frac{1}{6}s-h$.

@@

We observe that the minimum required stake for halting the blockchain in the Argennon protocol will be higher, as
long as the
following inequality holds:
\[
    \frac{1}{4}(s-d)-h > \frac{1}{3}s-(d+h)\ \cdot
\]
So if $d>\frac{1}{9}s$, the minimum required stake for halting the blockchain is higher in the
Argennon protocol and the value of $h$ does not matter.
